Won’t you be my neighboR?

### 2019-05-21 msu-workshop-2019.Rmd

@@

- [Jesse Mostipak](https://twitter.com/kierisi)
- [Alison Hill](https://twitter.com/apreshill)
- [Hadley Wickham](https://twitter.com/hadleywickham)
- [Daniel Anderson](https://twitter.com/datalorax_)
- [Mara Averick](https://twitter.com/dataandme)
- [Thomas Mock](https://twitter.com/thomas_mock)
- [Angela Li](https://twitter.com/CivicAngela)
- [R4DS community](https://twitter.com/R4DScommunity)
- [#tidytuesday](https://twitter.com/hashtag/TidyTuesday?src=hash)
- [#rstats](https://twitter.com/hashtag/rstats?src=hash)
- [David Robinson](https://twitter.com/drob)
- [Julia Silge](https://twitter.com/juliasilge)
- [Gabriela de Quieroz](https://twitter.com/gdequeiroz)
- [Joshua Rosenberg](https://twitter.com/jrosenberg6432)
- [Emily Bovee](https://twitter.com/ebovee09)

>>>>

# rmarkdown::render("msu-workshop-2019.rmd", output_file = 'index.html')

@@

- [Jesse Mostipak](https://twitter.com/kierisi)
- [Alison Hill](https://twitter.com/apreshill)
- [Hadley Wickham](https://twitter.com/hadleywickham)
- [Daniel Anderson](https://twitter.com/datalorax_)
- [Mara Averick](https://twitter.com/dataandme)
- [Thomas Mock](https://twitter.com/thomas_mock)
- [Angela Li](https://twitter.com/CivicAngela)
- [R4DS community](https://twitter.com/R4DScommunity)
- [#tidytuesday](https://twitter.com/hashtag/TidyTuesday?src=hash)
- [#rstats](https://twitter.com/hashtag/rstats?src=hash)
- [David Robinson](https://twitter.com/drob)
- [Julia Silge](https://twitter.com/juliasilge)
- [Gabriela de Quieroz](https://twitter.com/gdequeiroz)
- [Joshua Rosenberg](https://twitter.com/jrosenberg6432) and [Emily Bovee](https://twitter.com/ebovee09) (of course! :)
